% ************************** Thesis Acknowledgements *****************************

\begin{acknowledgements}      


First, I would like to thank my supervisor, Carl Rasmussen, for so much advice and encouragement.
It was wonderful working with someone who has spent many years thinking deeply about the business of modeling.
Carl was patient while I spent the first few months of my PhD chasing half-baked ideas, and then gently suggested a series of ideas which actually worked.

I'd also like to thank my advisor, Zoubin Ghahramani, for providing much encouragement, support, feedback and advice, and for being an example.
%As well, one of the best things about the lab was that it was constantly populated with interesting visitors, thanks mainly to Zoubin.
I'm also grateful for Zoubin's efforts to constantly populate the lab with interesting visitors.

Thanks to Michael Osborne, whose thesis was an inspiration early on, and to Roman Garnett for being a sane third party.
Sinead Williamson, Peter Orbanz and John Cunningham gave me valuable advice when I was still bewildered.
Ferenc Husz\'ar and Dave Knowles made it clear that constantly asking questions was the right way to go.

Tom Dean and Greg Corrado made me feel at home at Google.
Philipp Hennig was a mentor to me during my time in T\"{u}bingen, and demonstrated an inspiring level of effectiveness.
Who else finishes their conference papers with entire days to spare?
I'd also like to thank Ryan Adams for hosting me during my visit to Harvard, for our enjoyable collaborations, and for building such an awesome group.
Josh Tenenbaum's broad perspective and enthusiasm made the projects we worked on very rewarding.
The time I got to spend with Roger Grosse was mind-expanding -- he constantly surprised me by pointing out basic unsolved questions about decades-old methods, and had extremely high standards for his own work.

I'd like to thank Andrew McHutchon, Konstantina Palla, Alex Davies, Neil Houlsby, Koa Heaukulani, Miguel Hern\'{a}ndez-Lobato, Yue Wu, Ryan Turner, Roger Frigola, Sae Franklin, David Lopez-Paz, Mark van der Wilk and Rich Turner for making the lab feel like a family.
I'd like to thank James Lloyd for many endless and enjoyable discussions, and for keeping a level head even during the depths of deadline death-marches.
Christian Steinruecken showed me that amazing things are hidden all around.

Thanks to Mel for reminding me that I needed to write a thesis, for supporting me during the final push, and for her love.

My graduate study was supported by the National Sciences and Engineering Research Council of Canada, the Cambridge Commonwealth Trust, Pembroke College, a grant from the Engineering and Physical Sciences Research Council, and a grant from Google.

\end{acknowledgements}
